Network Configuration Synthesis with Abstract Topologies

### 2016-11-06 paper/abstraction/appendix.tex
update substitution proof in appendix

  \end{minipage}
  %
  ~~
  \vrule
  ~~
  %
  \begin{minipage}[t]{.5\linewidth}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{l}
     \textbf{compile}_\textbf{ABGP}(PG,ord) = \{ \\
     ~~~~~ \{ l \rightarrow rc ~\vert \\
     ~~~~~~~~~ l \in internal(V) \\
     ~~~~~~~~~ m = (l,q_m) \in PG, \\
     ~~~~~~~~~ in = \{ b_i ~\vert~ n_i = (b_i,q_n) \in \text{adjIn}(PG,m) \} \\
     ~~~~~~~~~ out = \{ c ~\vert~ (c,\dots) \in \text{adjOut}(PG,m) \} \\
     ~~~~~~~~~ rc = ord(m) : (in,q_n) \rightarrow (out,q_m) \\

     ~~~~~ \}
  \end{array} \]%

@@

\[ \begin{array}{rcl}
     con(l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k,m) 
        & = & 
        \{ x \rightarrow con(rc_i,m)  ~\vert~ x \in f^{-1}(l_i) \}
        \\
     con(t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k,m) 
        & = &  
        \{ pfx \rightarrow con(pc_i,m) ~\vert~ pfx \in m(t_i) \}
        \\
     con(ma_1, \dots, ma_k,m) 
        & = &
        con(ma_1,m), \dots, con(ma_k,m)
        \\
     con(n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3),m) 
        & = & 
        n_1 : (con({ns}_1,m), n_2) \rightarrow (con({ns}_2,m),n_3)
        \\
     con(\{ l_1, ~\dots,~ l_k \}, m) 
        & = &  
        \bigcup ~ \{ f^{-1}(l_i) \}
        \\
\end{array} \]

@@

>>>>

  \end{minipage}
  %
  ~~
  \vrule
  ~~
  %
  \begin{minipage}[t]{.5\linewidth}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{l}
     \textbf{compile}_\textbf{ABGP}(PG,ord) = \\
     ~~~~~ \{ l \rightarrow rc ~\vert \\
     ~~~~~~~~~ l \in internal(V) \\
     ~~~~~~~~~ m = (l,q_m) \in PG, \\
     ~~~~~~~~~ in = \{ b_i ~\vert~ n_i = (b_i,q_n) \in \text{adjIn}(PG,m) \} \\
     ~~~~~~~~~ out = \{ c ~\vert~ (c,\dots) \in \text{adjOut}(PG,m) \} \\
     ~~~~~~~~~ rc = ord(m) : (in,q_n) \rightarrow (out,q_m) \\
     ~~~~~ \}
  \end{array} \]%

@@

\[ \begin{array}{rcl}
     con(l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k,m) 
        & = & 
        \{ x \rightarrow con(rc_i,x,m)  ~\vert~ x \in f^{-1}(l_i) \}
        \\
     con(t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k,x,m) 
        & = &  
        \{ pfx \rightarrow con(pc_i,x,m) ~\vert~ pfx \in m(t_i) \}
        \\
     con(ma_1, \dots, ma_k,x,m) 
        & = &
        con(ma_1,x,m), \dots, con(ma_k,x,m)
        \\
     con(n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3),x,m) 
        & = & 
        n_1 : ( con({ns}_1,E^{-1},x,m), n_2) \rightarrow (con({ns}_2,E,x,m),n_3)
        \\
     con(\{ l_1, ~\dots,~ l_k \}, R, x, m) 
        & = &  
        \bigcup ~ \{ f^{-1}(l_i) \} \cap R
        \\
\end{array} \]

@@

\subsection{Substitution}

\begin{defn}
  The previous theorem tells us that the total ordering between node preferences is preserved under the lifted graph homomorphism $f_{pg}$. 
  We use this fact to define an ordering ($ord : V \rightarrow \mathbb{N}$) that maps product graph nodes to numbers reflecting the total ordering such that $ord(m) = ord(f(m))$ for all product graph nodes $m$.
\end{defn}

\begin{thm}
  $con(compile_{ABGP}(compile_{PG}(pol))) = compile_{ABGP}(compile_{PG}(con(pol)))$

    We know from the previous theorems the following:

    \[ \begin{array}{lll}
       PG^A, ord^A      &=& compile_{PG}(pol) \\
       PG, ord          &=& compile_{PG}(con(pol)) \\
    \end{array} \]%

    where for all product graph nodes $m$ we have $ord(m) = ord^A(f(m))$. Therefore we must prove:

    $$compile_{ABGP}(PG,ord) = con(compile_{ABGP}(PG^A,ord^A))$$

    \ryan{need to worry about prefixes}

    \[ \begin{array}{l}
       \textbf{compile}_\textbf{ABGP}(PG,ord) = \\
       ~~~~~ \{ l \rightarrow rc ~\vert \\
       ~~~~~~~~~ l \in internal(V) \\
       ~~~~~~~~~ m = (l,q_m) \in PG, \\
       ~~~~~~~~~ in = \{ b_i ~\vert~ n_i = (b_i,q_n) \in \text{adjIn}(PG,m) \} \\
       ~~~~~~~~~ out = \{ c ~\vert~ (c,\dots) \in \text{adjOut}(PG,m) \} \\
       ~~~~~~~~~ rc = ord(m) : (in,q_n) \rightarrow (out,q_m) \\
       ~~~~~ \}
    \end{array} \]%

    \[ \begin{array}{l}
       \textbf{compile}_\textbf{ABGP}(PG,ord) = \\
       ~~~~~ \{ l \rightarrow rc ~\vert \\
       ~~~~~~~~~ l \in internal(V) \\
       ~~~~~~~~~ m = (l,q_m) \in PG, \\
       ~~~~~~~~~ in = \{ b_i ~\vert~ n_i = (b_i,q_n) \in \text{adjIn}(PG,m) \} \\
       ~~~~~~~~~ out = \{ c ~\vert~ (c,\dots) \in \text{adjOut}(PG,m) \} \\
       ~~~~~~~~~ rc = ord^A(f(m)) : (in,q_n) \rightarrow (out,q_m) \\
       ~~~~~ \}
    \end{array} \]%

    \[ \begin{array}{l}
       \textbf{compile}_\textbf{ABGP}(PG^A,ord^A) = \\
       ~~~~~ \{ l \rightarrow rc ~\vert \\
       ~~~~~~~~~ l \in internal(V) \\
       ~~~~~~~~~ M = (l,q_M) \in PG^A, \\
       ~~~~~~~~~ in = \bigcup \{ f^{-1}(b_i) ~\vert~ N_i = (b_i,q_N) \in \text{adjIn}(PG^A,M) \} \cap E^{-1} \\
       ~~~~~~~~~ out = \bigcup \{ f^{-1}(c) ~\vert~ (c,\dots) \in \text{adjOut}(PG^A,M) \}) \cap E \\
       ~~~~~~~~~ rc = ord^A(M) : (in,q_N) \rightarrow (out,q_M)) \\
       ~~~~~ \}
    \end{array} \]%

    \[ \begin{array}{l}
       \textbf{compile}_\textbf{ABGP}(PG^A,ord^A) = \\
       ~~~~~ \{ l' \rightarrow rc ~\vert \\
       ~~~~~~~~~ l' \in f^{-1}(l) \\
       ~~~~~~~~~ l \in internal(V^A) \\
       ~~~~~~~~~ M = (l,q_M) \in PG^A, \\
       ~~~~~~~~~ in = \bigcup \{ f^{-1}(b_i) ~\vert~ N_i = (b_i,q_N) \in \text{adjIn}(PG^A,M) \} \cap E^{-1} \\
       ~~~~~~~~~ out = \bigcup \{ f^{-1}(c) ~\vert~ (c,\dots) \in \text{adjOut}(PG^A,M) \}) \cap E \\ 
       ~~~~~~~~~ rc = ord^A(M) : (in,q_N) \rightarrow (out,q_M)) \\
       ~~~~~ \}
    \end{array} \]%

    \[ \begin{array}{l}
       \textbf{compile}_\textbf{ABGP}(PG^A,ord^A) = \\
       ~~~~~ \{ l' \rightarrow rc ~\vert \\
       ~~~~~~~~~ l' \in f^{-1}(l) \\
       ~~~~~~~~~ l \in internal(V^A) \\
       ~~~~~~~~~ M = (l,q_M) \in PG^A, \\
       ~~~~~~~~~ in = con(\{ b_i ~\vert~ N_i = (b_i,q_N) \in \text{adjIn}(PG^A,M) \}) \\
       ~~~~~~~~~ out = con(\{ c ~\vert~ (c,\dots) \in \text{adjOut}(PG^A,M) \}) \\
       ~~~~~~~~~ rc = ord^A(M) : (in,q_N) \rightarrow (out,q_M)) \\
       ~~~~~ \}
    \end{array} \]%

    \[ \begin{array}{l}
       \textbf{compile}_\textbf{ABGP}(PG^A,ord^A) = \\
       ~~~~~ \{ l' \rightarrow rc ~\vert \\
       ~~~~~~~~~ l' \in f^{-1}(l) \\
       ~~~~~~~~~ l \in internal(V^A) \\
       ~~~~~~~~~ M = (l,q_M) \in PG^A, \\
       ~~~~~~~~~ in = \{ b_i ~\vert~ N_i = (b_i,q_N) \in \text{adjIn}(PG^A,M) \} \\
       ~~~~~~~~~ out = \{ c ~\vert~ (c,\dots) \in \text{adjOut}(PG^A,M) \} \\
       ~~~~~~~~~ rc = ord^A(M) : (con(in),q_N) \rightarrow (con(out),q_M)) \\
       ~~~~~ \}
    \end{array} \]%

    \[ \begin{array}{l}
       \textbf{compile}_\textbf{ABGP}(PG^A,ord^A) = \\
       ~~~~~ \{ l' \rightarrow rc ~\vert \\
       ~~~~~~~~~ l' \in f^{-1}(l) \\
       ~~~~~~~~~ l \in internal(V^A) \\
       ~~~~~~~~~ M = (l,q_M) \in PG^A, \\
       ~~~~~~~~~ in = \{ b_i ~\vert~ N_i = (b_i,q_N) \in \text{adjIn}(PG^A,M) \} \\
       ~~~~~~~~~ out = \{ c ~\vert~ (c,\dots) \in \text{adjOut}(PG^A,M) \} \\
       ~~~~~~~~~ rc = con(ord^A(M) : (in,q_N) \rightarrow (out,q_M)) \\
       ~~~~~ \}
    \end{array} \]%

    \[ \begin{array}{l}
       \textbf{compile}_\textbf{ABGP}(PG^A,ord^A) = \\
       ~~~~~ \{ l' \rightarrow con(rc) ~\vert \\
       ~~~~~~~~~ l' \in f^{-1}(l) \\
       ~~~~~~~~~ l \in internal(V^A) \\
       ~~~~~~~~~ M = (l,q_M) \in PG^A, \\
       ~~~~~~~~~ in = \{ b_i ~\vert~ N_i = (b_i,q_N) \in \text{adjIn}(PG^A,M) \} \\
       ~~~~~~~~~ out = \{ c ~\vert~ (c,\dots) \in \text{adjOut}(PG^A,M) \} \\
       ~~~~~~~~~ rc = ord^A(M) : (in,q_N) \rightarrow (out,q_M) \\
       ~~~~~ \}
    \end{array} \]%

    \[ \begin{array}{l}
       con(\textbf{compile}_\textbf{ABGP}(PG^A,ord^A) = \\
       ~~~~~ \{ l \rightarrow rc ~\vert \\
       ~~~~~~~~~ l \in internal(V^A) \\
       ~~~~~~~~~ M = (l,q_M) \in PG^A, \\
       ~~~~~~~~~ in = \{ b_i ~\vert~ N_i = (b_i,q_N) \in \text{adjIn}(PG^A,M) \} \\
       ~~~~~~~~~ out = \{ c ~\vert~ (c,\dots) \in \text{adjOut}(PG^A,M) \} \\
       ~~~~~~~~~ rc = ord^A(M) : (in,q_N) \rightarrow (out,q_M) \\
       ~~~~~ \})
    \end{array} \]%
